Four reasons your build is slow

### 2019-01-17 paper.tex
fix missing ref
missing cite
work on unnecessarily sequential section

If this call is no longer part of the span, the new span is similarly dominated by another single call to cc;
see fig. \ref{code:cc2}.
\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc \$(FLAGS)
  common/debug.c
  \textrm{\emph{29 more .c files}}
  -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{Verbatim}
\caption{A long running cc command which was responsible for aproximately 100\% of zstd's span when \ref{code:cc1} was not a membe rof the span.
This command compiled and linked 30 files.}
\label{code:cc2}
\end{figure}

If neither of these calls are members of the build's span, then our tool predicts the span would be
approximately 7.2 seconds rather than 39 seconds, as with the original span, or 37 seconds, as with the second span.
This is about an 80\% reduction in the build's span, and the parallelism improves from 2.98 to 16.

@@

Makefiles are a collection of rules which describe how to build targets \cite{gnumakemanual}.
Each rule consists
of a a series of prerequisites and a series of recipes which are run to build the target.  The
prerequisites can be built in parallel, but the recipes must be run in the order they are listed.  So,
the author of a makefile can directly impact the potential parallelism of the build by
how they organize their makefile.

In the previous section we discussed zstd's build, which turned out to be unnecessarily sequential
because two single shell calls which compiled and linked many files at once could be broken up
into many parallel compilation jobs which could then be linked after.  These two commands could
have been written as follows in fig. \ref{code:cc5} and fig. \ref{code:cc6} respectively, instead of as they were
originally in fig. \ref{code:cc1} and fig. \ref{code:cc2} and would have resulted in the same
build performance.

\begin{figure}[H]
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc \$(FLAGS) ../lib/common/debug.c
   -o ../lib/common/debug.o
\textrm{\emph{26 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -o zstd
\end{Verbatim}
  \caption{An alternative to the code in fig. \ref{code:cc1}. Each file is compiled individually
    as its own recipe, followed by a recipe to link the object files together.  This has the same
    performance as the original command.}
\label{code:cc5}
\end{figure}

\begin{figure}[H]
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc \$(FLAGS) common/debug.c -o common/debug.o1
\textrm{\emph{29 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -shared
   -o libzstd.so.1.3.7
\end{Verbatim}
  \caption{An alternative to the code in fig. \ref{code:cc2}. Each file is compiled individually
    as its own recipe, followed by a recipe to link the object files together.  This has the same
    performance as the original command.}
\label{code:cc6}
\end{figure}

To diagnose this problem using our tool, the user can once again calculate the span of the build
graph and look at what targets and shell calls constitute the span.  In this case the span is
made up of many short running compilation jobs.  To check if these compilation jobs may run in
parallel, our tool will take the original graph, the collected strace data, and build a new graph
as described in section \ref{sec:revisegraphs}.  The span of the new graph can then be compared
to the span of the old graph; if the span of the new graph is less than the span of the old graph,
then the original graph was unnecessarily sequential.  The allow this build to run faster in the
future, the developer can rewrite the makefile to reflect the organization of the build in
the new graph.

In the case of zstd, when built with strace; the calculated work for the original graph is 133
seconds and the span is 45 seconds; which means a parallelism of 2.95.  When this graph is
rebuilt using strace data and the span is recalculated, it is 8 seconds, which matches with the
predictions and observations from section \ref{sec:expensive}.

>>>>

If this call is no longer part of the span, the new span is similarly dominated by another single call to cc;
see fig. \ref{code:cc2}.
\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc \$(FLAGS)
  common/debug.c
  \textrm{\emph{29 more .c files}}
  -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{Verbatim}
\caption{A long running cc command which was responsible for aproximately 100\% of zstd's span when \ref{code:cc1} was not a membe rof the span.
This command compiled and linked 30 files.}
\label{code:cc2}
\end{figure}
If neither of these calls are members of the build's span, then our tool predicts the span would be
approximately 7.2 seconds rather than 39 seconds, as with the original span, or 37 seconds, as with the second span.
This is about an 80\% reduction in the build's span, and the parallelism improves from 2.98 to 16.

@@

Makefiles are a collection of rules which describe how to build targets \cite{gnumakemanual},
and each rule consists
of a a series of prerequisites and a series of recipes which are run to build the target.  The
prerequisites can be built in parallel, but the recipes must be run in the order they are listed.  So,
the author of a makefile can directly impact the potential parallelism of the build by
how they organize their makefile.  It is possible to unnecessarily list things as recipes that
could have run in parallel.  Here we will look at an example of this and how our tool can
discover that these recipes don't actually need to run in parallel.

In the previous section we discussed zstd's build, which turned out to be unnecessarily sequential
because two single shell calls which compiled and linked many files at once could be broken up
into many parallel compilation jobs which could then be linked after.  These two commands could
have been written as follows in fig. \ref{code:cc5} and fig. \ref{code:cc6} respectively, instead of as they were
originally in fig. \ref{code:cc1} and fig. \ref{code:cc2} and would have resulted in the same
build performance, but would make it possible for our tool to detect that they are unnecessarily
sequential.

The following code is an alternative to the code in fig. \ref{code:cc1}. Each file is compiled individually
as its own recipe, followed by a recipe to link the object files together.  This has the same
performance as the original command.
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc \$(FLAGS) ../lib/common/debug.c
   -o ../lib/common/debug.o
\textrm{\emph{26 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -o zstd
\end{Verbatim}

The following code is an alternative to the code in fig. \ref{code:cc2}. Each file is compiled individually
  as its own recipe, followed by a recipe to link the object files together.  This has the same
  performance as the original command.
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc \$(FLAGS) common/debug.c -o common/debug.o1
\textrm{\emph{29 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -shared
   -o libzstd.so.1.3.7
\end{Verbatim}

  These recipes compiling individual files can run in parallel, as shown in the previous section,
  and our tool can detect this by using the build graph and the system call information gathered
  by strace and applying the methods described in section \ref{revisegraphs}.  When the span
  of the new graph is calculated it reflects the fact that these compilations can occur in
  parallel and is 8 seconds rather than the original 45 seconds; these times are longer than
  those mentioned in the previous section because strace inflates the running time of the
  commands it traces.
